Package Documentation

### 2022-07-14 quarto-doc/pkg_doc.qmd
Update quarto doc. Re #97

+---------------+----------------------+----------------------+
| Label         | Name                 | Levels               |
+===============+======================+======================+
| *a*           | Age group            | 15--49\              |
|               |                      | 50--69               |
+---------------+----------------------+----------------------+
| *g*           |                      | Male\                |
|               |                      | Female               |
+---------------+----------------------+----------------------+
| *h*           | Disease              |                      |
+---------------+----------------------+----------------------+
| *i*           | Individual index     |                      |
+---------------+----------------------+----------------------+
| *j*           | Trip index           |                      |
+---------------+----------------------+----------------------+
| *m*           | Transport mode       | walk\                |
|               |                      | cycling (cyc.)\      |
|               |                      | bus\                 |
|               |                      | car\                 |
|               |                      | motorbike (mot.)\    |
|               |                      | goods vehicles (GV)\ |
|               |                      | subway (sub.)        |
+---------------+----------------------+----------------------+
| *o*           | Outcome              | Death\               |
|               |                      | YLL                  |
+---------------+----------------------+----------------------+
| *s*           | Scenario             | 3                    |
+---------------+----------------------+----------------------+
| *w*           | AP RR hyperparameter | 1, 2, 3, 4           |
+---------------+----------------------+----------------------+
| *x*           | PA RR hyperparameter | 1, 2, 3              |
+---------------+----------------------+----------------------+
| *z*           | PA dose              |                      |
+---------------+----------------------+----------------------+

@@

+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+

@@

+:==========================================+=================================================================+:===================================+===============================+====================+

@@

+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+
| $I _ {a,g,m_{\                            | Fatalities table                                                | Constant                           | INJURY_TABLE                  | Setting            |
| text{vi c} },m_{\text{str}}}$             |                                                                 |                                    |                               |                    |
+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+

@@

+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+
| $\                                        | Vehicle emission inventory                                      | Constant or Dirichlet              | EMISSION_INVENTORY            | Setting            |
| g amma_{m}$                               |                                                                 |                                    |                               |                    |
+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+

@@

+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+
| $\                                        | Quantiles for AP RR functions                                   | 0.5 or Unif(0,1)                   | AP_DOSE_R ESPONSE\_ QUANTILE  | Model              |
| xi_{h,w}$                                 |                                                                 |                                    |                               |                    |
+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+

@@

+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+
| $\                                        | Confidence in PA survey                                         | 1                                  | BACKGROUND_PA_C ONFIDENCE     | Setting            |
| tilde{Y}$                                 |                                                                 |                                    |                               |                    |
+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+

@@

### Scenarios

@@

We use each person's exposure to PM2.5 ($\check{W}_{i,s}$) to calculate their relative risk of five diseases (IHD, lung cancer, COPD, stroke, LRI), using curves parametrised by four disease-specific variables [@Burnett2014]. Of the five diseases, two (IHD and stroke) have parameters specific to age groups starting at age 25.[^2] The other three (lung cancer, LRI and COPD) have one set of parameters for all ages.

@@

The curves are in the form of samples of the set of four parameters. We model the densities of these samples (using a quantile for parameter 3, kernel density estimation for parameter 2, and GAMs for parameters 1 and 4)[^3] in order to draw either the median or random samples via their quantiles ($\xi_{h,w}$) as follows:

@@

::: landscape
# Tabulated ITHIM equations {#tableequations}

>>>>

+-------------+----------------------+-------------------------------+
| Label       | Name                 | Levels                        |
+=============+======================+===============================+
| *a*         | Age group            | 15--69 (five years age group) |
+-------------+----------------------+-------------------------------+
| *g*         |                      | Male\                         |
|             |                      | Female                        |
+-------------+----------------------+-------------------------------+
| *h*         | Disease              |                               |
+-------------+----------------------+-------------------------------+
| *i*         | Individual index     |                               |
+-------------+----------------------+-------------------------------+
| *j*         | Trip index           |                               |
+-------------+----------------------+-------------------------------+
| *m*         | Transport mode       | walk\                         |
|             |                      | cycling (cyc.)\               |
|             |                      | bus\                          |
|             |                      | car\                          |
|             |                      | motorbike (mot.)\             |
|             |                      | goods vehicles (GV)\          |
|             |                      | subway (sub.)                 |
+-------------+----------------------+-------------------------------+
| *o*         | Outcome              | Death\                        |
|             |                      | YLL                           |
+-------------+----------------------+-------------------------------+
| *s*         | Scenario             | 3                             |
+-------------+----------------------+-------------------------------+
| *w*         | AP RR hyperparameter | 1, 2, 3, 4                    |
+-------------+----------------------+-------------------------------+
| *x*         | PA RR hyperparameter | 1, 2, 3                       |
+-------------+----------------------+-------------------------------+
| *z*         | PA dose              |                               |
+-------------+----------------------+-------------------------------+

@@

+-------------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+

@@

+:================================================+=================================================================+:===================================+===============================+====================+

@@

+-------------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+
| $I _ {a,g,m_{\  text{vi c} },m_{\text{str}}}$   | Fatalities table                                                | Constant                           | INJURY_TABLE                  | Setting            |
+-------------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+

@@

+-------------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+
| $\  g amma_{m}$                                 | Vehicle emission inventory                                      | Constant or Dirichlet              | EMISSION_INVENTORY            | Setting            |
+-------------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+

@@

+-------------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+
| $\  xi_{h,w}$                                   | Quantiles for AP RR functions                                   | 0.5 or Unif(0,1)                   | AP_DOSE_R ESPONSE\_ QUANTILE  | Model              |
+-------------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+

@@

+-------------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+
| $\  tilde{Y}$                                   | Confidence in PA survey                                         | 1                                  | BACKGROUND_PA_C ONFIDENCE     | Setting            |
+-------------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+

@@

### Scenarios {#scenarios}

@@

We use each person's exposure to PM2.5 ($\check{W}_{i,s}$) to calculate their relative risk of seven causes/diseases (all-cause mortality, IHD, stroke, COPD, LRI, Lung cancer and Type 2 Diabetes (T2D)). These diseases operate in three levels. The Level 1 is for all-cause mortality. The Level 2 combines IHD and stroke to CHD, and COPD, LRI, Lung cancer and T2D as respiratory disease mortality, and then in level 3, we have all diseases separately. Of the five diseases, two (IHD and stroke) have parameters specific to age groups starting at age 25.[^2] The other three (lung cancer, LRI and COPD) have one set of parameters for all ages.

@@

![AP disease levels](images/ap-levels-min.png)The curves are in the form of samples of the set of four parameters. We model the densities of these samples (using a quantile for parameter 3, kernel density estimation for parameter 2, and GAMs for parameters 1 and 4)[^3] in order to draw either the median or random samples via their quantiles ($\xi_{h,w}$) as follows:

@@

::: landscape \# Tabulated ITHIM equations {#tableequations}
